An Integrated Framework for Robust Estimation, Prediction and Control

### 2019-12-05 main.tex
Update vector form

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{natbib}
\usepackage{caption}
\usepackage{blkarray}
\usepackage{todonotes}
\usepackage{mathtools}

@@

\subsection{Vector formulation}
In the general case, we denote the weighted version of the Frobenius inner product Frobenius norm as $\inp{M}{N}_{F,\Sigma} = \Tr (M^T \Sigma N)$ and $\|M\|_{F,\Sigma}^2 = \inp{M}{M}_{F,\Sigma}$.

@@

\begin{theorem}
\begin{equation}
    \label{eq:vector_rls}
    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \begin{bmatrix}\inp{\Phi_{[N],i}^T}{Y_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}
\end{equation}
where $\Phi_{[N],i}\in\Real^{p\times d}$ is the $i^\text{th}$ component of $\Phi_{[N]}$ along the first component, and
\begin{equation*}
    G_{N, \lambda} = \begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Phi_{[N],j}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i,j\in[d]^2} + \lambda \Sigma_d \in \Real^{d\times d}.
\end{equation*}
\end{theorem}

@@

Using the Cauchy-Schwartz inequality, we get:
\begin{align*}
    |x^T\theta_{N,\lambda}  -x^T\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}\right)
\end{align*}
\todo[inline]{The first term is a $\Real^d$ vector whose coefficients are inner product of matrices (a sum along time and $p$ dimensions). How to analyze its concentration?}

@@

\bibliographystyle{plainnat}
\bibliography{references}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{caption}
\usepackage{blkarray}
\usepackage{todonotes}
\usepackage{mathtools}
\usepackage[backend=biber,style=authoryear,natbib=true,url=false]{biblatex}

\addbibresource{references.bib}

@@

\subsection{Vector formulation}
In the general case, we denote the weighted version of the Frobenius inner product and Frobenius norm as $\inp{M}{N}_{F,\Sigma} = \Tr (M^T \Sigma N)$ and $\|M\|_{F,\Sigma}^2 = \inp{M}{M}_{F,\Sigma}$.

@@

\begin{theorem}[Regularized solution] The solution to \eqref{eq:regression_min} is:
\begin{equation}
    \label{eq:vector_rls}
    \theta_{N,\lambda} = G_{N, \lambda}^{-1} \begin{bmatrix}\inp{\Phi_{[N],i}^T}{Y_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}
\end{equation}
where $\Phi_{[N],i}\in\Real^{p\times d}$ is the $i^\text{th}$ component of $\Phi_{[N]}$ along the first dimension, and
\begin{equation*}
    G_{N, \lambda} = \begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Phi_{[N],j}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i,j\in[d]^2} + \lambda \Sigma_d \in \Real^{d\times d}.
\end{equation*}
\end{theorem}

@@

Using the Cauchy-Schwartz inequality, we get:
\begin{align*}
    |x^T\theta_{N,\lambda}  -x^T\theta| &\leq \|x\|_{G_{N, \lambda}^{-1}}\left(\left\|\begin{bmatrix}\inp{\Phi_{[N],i}^T}{\Omega_{[N]}^T}_{F, \Sigma_p^{-1}}\end{bmatrix}_{i\in[d]}\right\|_{G_{N, \lambda}^{-1}} + \lambda\|\Sigma_d\theta\|_{G_{N, \lambda}^{-1}}\right)
\end{align*}
\todo[inline]{EL: The first term is a $\Real^d$ vector whose coefficients are inner product of matrices (a sum along both the time $N$ and $p$ dimensions). How to analyze its concentration? For comparison, in \citep{Abbasi2011} $X^T\eta$ was a  $\Real^d$ vector whose coefficients were inner product of vectors $(X_i^T\eta)_i\in[d]$ (a sum over time $N$)}

@@

\printbibliography
